Sorting by Reversals

### 2020-07-14 paper.tex
update paper abstract

\begin{abstract}
    A reversal is a transformation that inverses the order of elements of a permutation. Sorting by reversals is the problem of finding the shortest sequence of reversals transforming a permutation to the identity. The length of such a sequence is said to be the reversal distance of that permutation. In this paper we introduce important concepts used in the literature on this topic. In particular, we introduce the fundamental relationship between the reversal distance and the number of alternating cycles in a cycle decomposition of a suitably-defined bi-colored graph. Then, a $3/2$-approximation is discussed in detail.
\end{abstract}

@@

\begin{definition}
\textit{Sorting by reversals (MIN-SBR)} then is the problem of determining the reversal distance between some permutation $\pi \in S_n$ and $id$. The reversal distance is denoted by $d(\pi)$. We say that a sequence of reversals transforming $\pi$ into $id$, \textit{sorts} $\pi$.
\end{definition}

>>>>

\begin{abstract}
    A reversal is a transformation that inverses the order of some consecutive elements of a permutation. Sorting by reversals is the problem of finding the shortest sequence of reversals transforming a permutation to the identity. The length of such a sequence is said to be the reversal distance of that permutation. In this paper we introduce important concepts used in the literature on this topic. In particular, we introduce the fundamental relationship between the reversal distance and the number of alternating cycles in a cycle decomposition of a suitably-defined bi-colored graph. Then, a $3/2$-approximation obtained by \citeauthor*{Christie1998} is discussed in detail.
\end{abstract}

@@

\begin{definition}
\textit{Sorting by reversals (MIN-SBR)} then is the problem of determining the reversal distance between some permutation $\pi \in S_n$ and $id$. The reversal distance is denoted by $d(\pi)$. A sequence of reversals transforming $\pi$ into $id$, \textit{sorts} $\pi$.
\end{definition}
